Supercritical fluid extraction of essential oil from chamomile seeds: experiments, modelling, and parameter estimation

### 2024-02-12 SFE_article_Parameter_Estimation - Chamomile/Sections/Parameter_estimation.tex
12.02

	{\footnotesize
		\begin{equation} \label{EQ: Objective_function}
			\ln L = -\cfrac{n}{2}  \ln \sqrt{2 \pi \sigma^2} 
			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} \right]^2 }{2 {\color{black} \sigma}^2}
		\end{equation}
	}

@@

	where $\hat{{\color{black} \theta}}$ is as maximum likelihood estimator, ${\color{black} \theta}^{lb}$ define the minimal value of ${\color{black} \theta}$ and ${\color{black} \theta}^{ub}$ is the maximum value of ${\color{black} \theta}$.

@@

	\begin{itemize}
		\item Partition coefficient:\qquad\quad\qquad$k_m$
		\item Internal diffusion coefficient: \quad$D_i^R$
		%\item Axial diffusion coefficient: \qquad$D_e^M$
		\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
		\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
	\end{itemize}

@@

 	\begin{table}[h]
		\adjustbox{max width=\columnwidth}{%
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $\sigma$[-] \\  \hline
				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		& 0 \\ 
				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	& $+\infty$\\ 
				Initial guesses	&0.1-10		& $0.1-10$ 			& 0 		   		& 0.1-10		& 0.01 \\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

>>>>

	{\footnotesize
		\begin{equation} \label{EQ: Objective_function}
			\ln L = -\cfrac{n}{2}  \ln \left(2 \pi \sigma^2\right) 
			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} \right]^2 }{2 {\color{black} \sigma}^2}
		\end{equation}
	}

@@

	where $\hat{{\color{black} \theta}}$ is as maximum likelihood estimator, ${\color{black} \theta}^{lb}$ define the minimal value of ${\color{black} \theta}$, ${\color{black} \theta}^{ub}$ is the maximum value of ${\color{black} \theta}$ and $\sigma$ represents the standard deviation of the residuals (errors) between the observed data points and the model outputs.

@@

	\begin{itemize}
		\item Partition coefficient:\qquad\quad\qquad$k_m$
		\item Internal diffusion coefficient: \quad$D_i^R$
		\item Axial diffusion coefficient: \qquad$D_e^M$
		\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
		%\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
	\end{itemize}

@@

 	\begin{table}[h]
		\adjustbox{max width=\columnwidth}{%
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] \\  \hline
				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		\\ 
				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	\\ 
				Initial guesses	&0.1-10		& $0.1-10$ 			& 0.1-10   			& 0.1-10		\\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

### 2024-02-12 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
12.02

\section{Results}
\subfile{Sections/Results}

@@

This study presented basic aspects regarding the laboratory work for obtaining chamomile extracts using supercritical carbon dioxide at different operating conditions. A first-principle process model was developed based on governing equations. As a result of the literature review, the extraction kinetic model was selected and combined with the general mass balance equations. The values of unknown parameters in the process model were obtained by parameter estimation. The yield data from the experiments were compared against the yield generated by the model. The IPOPT solver was used to solve the maximum likelihood estimation. The process model was found to have good agreement with experimental yield curves. Later, the parameters found for each experiment were combined to obtain more general relationships. The correlations for diffusion and decay coefficients are presented as a function of fluid density or Reynolds number. It should be noted that obtained correlations have been prepared with a limited amount of data. These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis. Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.

>>>>

\section{Results}
\subfile{Sections/Results_Chamomile}

@@

%This study presented basic aspects regarding the laboratory work for obtaining chamomile extracts using supercritical carbon dioxide at different operating conditions. A first-principle process model was developed based on governing equations. As a result of the literature review, the extraction kinetic model was selected and combined with the general mass balance equations. The values of unknown parameters in the process model were obtained by parameter estimation. The yield data from the experiments were compared against the yield generated by the model. The IPOPT solver was used to solve the maximum likelihood estimation. The process model was found to have good agreement with experimental yield curves. Later, the parameters found for each experiment were combined to obtain more general relationships. The correlations for diffusion and decay coefficients are presented as a function of fluid density or Reynolds number. It should be noted that obtained correlations have been prepared with a limited amount of data. These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis. Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.
